---
title: <small>An introduction to digital open <br>research in clinical psychology</small>
author: <small>Matthias Weiler</small>
date: <small>30.03.2019</small>
output:
  revealjs::revealjs_presentation:
    theme: black
    center: TRUE
    self_contained: FALSE
    incremental: TRUE
    reveal_plugins: ["chalkboard"]
    reveal_options:
      chalkboard: 
      readonly: FALSE
---

# <small> What did we do last session?</small>

----

We had a tiny introduction to R

----

... played with data  
from Google trends

----

... and from the Hellenic  
Statistical Authority

----

Any questions or anything to add?



# <small>Last session's homework</small>

----

Who of you created your own  
data collection script?

----

... uploaded your script to GitHub?

----

Any questions regarding  
last session's homework?



# <small>Today:<br>Data analysis</small>

----

## <small>We will take a look at</small>

- t-test
- Kolmogorov-Smirnov Test
- Pearson's correlation
- R Notebooks for documentation

```{r cache=FALSE, echo=FALSE}
knitr::read_chunk('analysis/data_analysis.R')
```


# <small>Before we begin</small>

... we need to generate some data

```{r generate data}
```

----

Depending on our analysis  
will either need data in  
long or in wide format

----

## <small>Data in long format</small>

```{r show long data, echo=FALSE}
```

----

## <small>Data in wide format</small>

```{r show wide data, echo=FALSE}
```



# <small>Independent t-test</small>

----

t-test with data in long format

```{r t test long}
```

----

t-test with data in wide format

```{r t test wide}
```

----

t-test for groups with  
unequal variance

```{r t test unequal variance}
```

# <small>Kolmogorov-Smirnov Test</small>

----

The Kolmogorov-Smirnov Test  
uses data in wide format

```{r kolmogorov–smirnov test}
```



# <small>Pearson's correlation</small>

----

Pearson's correlation also  
uses data in wide format

```{r correlation}
```



# <small>R Notebooks</small>

----

Document your code! Else,  
others might not understand  
what you were doing

----

And by others I mean you in  
about three weeks from now

----

[Here](https://mrweiler.github.io/dosp-2019-06/notebook.html)
you can find an R Notebook  
of today's data analysis



# <small>Preview: next session</small>

----

"Data visualization"



# <small>Homework</small>

Add your team members  
as collaborators to  
your GitHub repository

----

Add your team members  
as contributors to your  
research projects in OSF



# <small>Any questions?</small>



# <small>Thank you for your attention</small>
