---
title: "My analysis"
output:
  html_document:
    df_print: paged
---

```{r cache=FALSE, echo=FALSE}
knitr::read_chunk('analysis/data_analysis.R')
```

## Generate data {.tabset}

First we need to generate some data:

```{r generate data}
```

### Long format

This is data in long format.

```{r show long data, echo=FALSE}
```

### Wide format

This is data in wide format.

```{r show wide data, echo=FALSE}
```

## Analyze data 

### T-Test {.tabset .tabset-fade .tabset-pills}

To analyze the data we can use an independent t-test.  

#### Long format

The t-test can be used on data in long format.

```{r t-test long}
```

#### Wide format

The t-test can be used on data in wide format.

```{r t-test wide}
```

#### Unequal variance

There is also a t-test for groups with unequal variance.

```{r t-test unequal variance}
```

### Kolmogorov-Smirnov Test

The Kolmogorov-Smirnov Test uses data in wide format.

```{r kolmogorov–smirnov test}
```

### Pearson's correlation

Pearson's correlation also uses data in wide format.

```{r correlation}
```
